Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/related-work.tex
[ paper ] fixed related work.

\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a
proof-reconstruction in \Agda for propositional logic. Its tool support
proof-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-flow as we presented in Section~\ref{ssec:workflow}.
Nonetheless, its approach
employs semantics for logic equivalences. We have avoided the use of
propositions meanings towards a future work to support other logics where a
syntactical approach plays an important role~(for an example of such logics, we
refer the reader to \cite{Agudelo-Agudelo2017}).
\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
prover for pure equational logic. As far as we know, no other proof-
reconstruction has been carried out in \Agda and with \Metis prover.

Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
we found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
certified checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
transform a proof produced by the first-order automatic theorem prover
\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof term.

>>>>

\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a
proof-reconstruction in \Agda for propositional logic. Its tool support
proof-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-flow as we presented in Section~\ref{ssec:workflow}.
Nonetheless, its approach
employs semantics for logic equivalences. We have avoided the use of
propositions meanings towards a future work to support other logics where a
syntactical approach plays an important role~(for an example of such logics, we
refer the reader to \cite{Agudelo-Agudelo2017}).
\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
prover for pure equational logic. As far as we know, no other
proof-reconstruction has been carried out neither in \Agda nor with \Metis prover.

Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
We found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
certified checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
transform a proof produced by the first-order automatic theorem prover
\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof term.
